Pillar 1 - Sequential Pattern Mining

### 2019-01-17 Pillar 1 - Sequential Pattern Mining.Rmd
low_grade high_grade threshold + evgueni file

@@

d_pass_sequence_transactions <- d_course %>%
  select(Type, Code, Letters) %>%
  filter(Type == "Elective",
         ! Letters %in% c("SKI", "PRO"),
         ! Letters %in% c("SAS", "SAH", "SAC")) %>%
  select(Code) %>%
  left_join(d_transcript, by = c("Code" = "Course Code")) %>%
  mutate(Outcome = 
           case_when( Grade=="NG"~"Fail", #if we don't do this NG satisfies the condition for pass v
                      Grade > 5.5 ~"Pass",
                              T~"Fail"),
         Low_grade =
           case_when(Grade=="NG"~"Sad", #if we don't do this NG satisfies the condition for pass v
                      Grade > fail_threshold ~"OK",
                              T~"Sad")
         ) %>%
  mutate(Item = paste(Code, Low_grade, sep = "_") ) %>% #Change for Outcome/Low_grade
  filter(!str_detect(Period, " to ")) %>% #filter courses that spann more than one period
  mutate( Time = paste(Year_numerical, Period, sep = ""),
          Time = as.double(Time)) %>%
  select(`Student ID Number`, Item, Time) %>%
  arrange(`Student ID Number`, Time) %>% #Note that integer identifiers must be positive and that transactions must be ordered by sequenceID and eventID.
  group_by(`Student ID Number`, Time) %>%
  summarize(list_course = list(Item)) %>% #if we run the code until here maybe its possible to use sequence_transactions <- as(sequence_transaction$list_course, "transactions")
  mutate(TransactionID = paste(`Student ID Number`, Time, sep = "_"))

@@

pass_rules <- ruleInduction(frequent_pass_trajectories, confidence = 0.1, #we need to play with the parameters.
                    control    = list(verbose = TRUE))
pass_rules_df <- as(pass_rules, "data.frame") %>%
  arrange(desc(lift))
```
Checking who failed
```{r}
pass_rules_df %>%
  separate(rule, into=c("LHS", "RHS"), sep = "=>", remove = T) %>% #remove= F to keep columns
  filter(str_detect(RHS, "_Sad")) %>%
  arrange(desc(confidence), desc(lift))
```

>>>>

```
#Data Exploration of Transcripts
```{r}
exploration <- d_transcript %>%
  mutate(Grade = case_when(Grade == "NG"~ "0.0",
                           T~Grade),
         Grade=as.double(Grade))
```

@@

d_pass_sequence_transactions <- d_course %>%
  select(Type, Code, Letters) %>%
  filter(Type == "Elective",
         ! Letters %in% c("SKI", "PRO"),
         ! Letters %in% c("SAS", "SAH", "SAC")) %>%
  select(Code) %>%
  left_join(d_transcript, by = c("Code" = "Course Code")) %>%
  mutate(Outcome = 
           case_when( Grade=="NG"~"Fail", #if we don't do this NG satisfies the condition for pass v
                      Grade > 5.5 ~"Pass",
                              T~"Fail"),
         Low_grade =
           case_when(Grade=="NG"~"low score", #if we don't do this NG satisfies the condition for pass v
                      Grade > fail_threshold ~"high score",
                              T~"low score")
         ) %>%
  mutate(Item = paste(Code, Low_grade, sep = "_") ) %>% #Change for Outcome/Low_grade
  filter(!str_detect(Period, " to ")) %>% #filter courses that spann more than one period
  mutate( Time = paste(Year_numerical, Period, sep = ""),
          Time = as.double(Time)) %>%
  select(`Student ID Number`, Item, Time) %>%
  arrange(`Student ID Number`, Time) %>% #Note that integer identifiers must be positive and that transactions must be ordered by sequenceID and eventID.
  group_by(`Student ID Number`, Time) %>%
  summarize(list_course = list(Item)) %>% #if we run the code until here maybe its possible to use sequence_transactions <- as(sequence_transaction$list_course, "transactions")
  mutate(TransactionID = paste(`Student ID Number`, Time, sep = "_"))

@@

pass_rules <- ruleInduction(frequent_pass_trajectories, confidence = 0.1, #we need to play with the parameters.
                    control    = list(verbose = TRUE))
pass_rules_df <- as(pass_rules, "data.frame") %>%
  arrange(desc(lift))
```
Checking who failed
```{r}
view_rules <- pass_rules_df %>%
  separate(rule, into=c("LHS", "RHS"), sep = "=>", remove = T) %>% #remove= F to keep columns
  filter(str_detect(RHS, "low score")) %>% #change so that it changes automatically
  arrange(desc(confidence), desc(lift))

write_csv(view_rules, "Data_Evgueni.csv")
```
